mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-05 thesis/thesis.tex
update

An approach of efficient software development is to use component-based techniques.
CBD (Component-Based Development) is a design technique for constituting reusable components \cite{Crnkovic:2005:CSE:1062455.1062631}.
Complex and large scale software systems can be developed efficiently using component-based techniques.
That is because software componentization provides high-reusability and easy verification.
It also makes a system flexible in extensions and specification changes.

@@

mruby on TECS is a component-based framework for running script program \cite{7153813}.
It is integrated two technologies.
One is mruby, which is a script language for embedded systems \cite{5959588}.
The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{4208825}.
TECS supports to effectively run mruby script language on embedded systems.
mruby on TECS also makes execution time 100 times faster than that of mruby.

This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
mruby on TECS has some problems at present.
One of these is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
Thus that is a big burden on developers.
Another new feature enables developers to run a multitask programs more easily.
Specifically, a cycle handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

@@

Ruby is a object-oriented script language.
As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
Ruby can run a program with fewer code lines than C language.
Ruby improves the productivity of a software development owing to not only simple grammar also object-oriented functions such as classes and methods, exceptions, and garbage collection.

@@

    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
        In the same way, {\it call} ports can be declared.
        Attributes and valuables follow the keyword attr and var respectively.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller{
    call sMotor cMotor;
};

celltype tMotor{
    entry sMotor eMotor;
    attr{
        int32_t attr = 100;
    };
    var{
        int32_t var;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}

    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
        To compose {\it cell}s a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor{
};

cell tCaller Caller{
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

As the target RTOS, TOPPERS/HRP2 \cite{6913200} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{6332346} and TOPPERS/ASP.

@@

There is a great difference between the execution time of mruby and C language.
According to  \cite{7153813}, mruby programs are several hundreds times slower than C programs.
The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
Thus it is difficult to use mruby for all of code.

@@

\subsection{Component of mruby bytecode loader using Bluetooth}
The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{7153813}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
This generated bytecode is prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
TOPPERS/HRP2 is described in \cite{6913200}.
The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
In this framework, ZMODEM \cite{forsberg1988zmodem} is used as a binary transfer protocol.

@@

Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of mruby bytecode loader using Bluetooth, which is like MrubyBluetooth1.
First, a pointer of {\it mrb\_state} structure is initialized.
{\it mrb\_state} is a set of states and global variables used in mruby.
Second, the bytecode of mruby libraries is read.
mruby libraries are a set of Ruby classes such as motor class and sensor class.
For example, motor class defines methods to rotate and stop a motor.
The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: {\it mrubyFile} and {\it irep}.
The {\it mrubyFile} indicates the program files of mruby libraries.
{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
The irep is the pointer of the array stored the bytecode of mruby libraries.
In short the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
Third, the bytecode of the mruby program transferred with Bluetooth is read .
The bytecode transmitted via Bluetooth is stored in an array of type uint8\_t, which is the same as type char.
The array is different from that of holding the mruby library bytecode.
Two bytecodes are read separately in the {\it mrb\_state}.
Finally, an mruby task runs.
When the mruby program is modified, only the bytecode of the modified program should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
    \caption{Control Flow of mruby bytecode loader using Bluetooth}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irep_lib=C_EXP("&$cell_global$_irep");
      uint8_t irep_app[COUNT_STK_T(TMAX_APP_BINARY_SIZE)] __attribute__((nocommon));
    };
};
\end{lstlisting}
\caption{Celltype Description for mruby bytecode loader using Bluetooth}
\label{celltype_mrubybluetooth}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main(CELLIDX idx)
{
  /* Declaration variables */
  mrb_state *mrb;
  mrbc_context *c;

  /* New interpreter instance */
  mrb = mrb_open();
  // Error Check for mrb_state

  /* New mruby context */
  c = mrbc_context_new(mrb);

  // Initialization of mruby TECS Bridge

  /* Receive the bytecode via Bluetooth */
  bluetooth_loader( ATTR_app );

  /* Load mruby library bytecode and run */
  mrb_load_irep_cxt(mrb, ATTR_lib, c);
  /* Load mruby application bytecode and run */
  mrb_load_irep_cxt(mrb, ATTR_app, c);

  if (mrb->exc) {
    /* Failure to execute */
    mrb_p(mrb, mrb_obj_value(mrb->exc));
    exit(0);
  }
  /* Free mruby context */
  mrbc_context_free(mrb, c);
  /* Free interpreter instance */
  mrb_close(mrb);
}

@@

\subsection{Component of Cyclic Handler}
Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the cyclic handler based on ITRON.
Cyclic handlers based on ITRON are described in detail \cite{ITRON_spec}.
The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
    \caption{Component Diagram of Cyclic Handler}
    \label{fig:cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
celltype tCyclicHandler {
    [inline] entry sCyclic eCyclic;
    call  siHandlerBody  ciBody;
    attr {
    	[omit] ATR    attribute = C_EXP("TA_NULL");
    	[omit] RELTIM cyclicTime;
    	[omit] RELTIM cyclicPhase = 0;
    };
};

celltype tCyclicMain{
    require tKernel.eiKernel;
    entry siHandlerBody eiBody;
    attr {
        PRI priority;
    };
};
    \end{lstlisting}
    \caption{Celltype Description of Cyclic Handler}
    \label{celltype_cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tCyclicHandler CyclicHandler{
    ciBody = CyclicMain.eiBody;
    attribute = C_EXP("TA_STA");
    cyclicTime = 1;
    cyclicPhase = 1;
};

cell tCyclicMain CyclicMain{
    priority =
        C_EXP("RITEVM_PRIORITY");
};
   \end{lstlisting}
    \caption{Build Description of Cyclic Handler}
    \label{build_cyclic_handler}
\end{figure}

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccc}
        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
        Lua \cite{Ierusalimschy:2007:EL:1238844.1238846} &            & -          & \checkmark &            \\
        Owl system \cite{180964}                         &            & -          & -          & \checkmark \\
        mruby \cite{5959588}                             &            &            & \checkmark &            \\
        mruby on TECS \cite{7153813}                     &            & \checkmark & \checkmark &            \\
        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}, the Owl system \cite{180964}, mruby \cite{5959588}, and mruby on TECS \cite{7153813}.

@@

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip \cite{python-on-a-chip}.
python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
GIL leads the limitation of the concurrency on multitasking.

@@

%%%%%%%%%%%%%
% Reference %
%%%%%%%%%%%%%
\bibliography{ref}

>>>>

An approach of efficient software development is to use component-based techniques.
CBD (Component-Based Development) is a design technique for constituting reusable components \cite{par:Crnkovic}.
Complex and large scale software systems can be developed efficiently using component-based techniques.
That is because software componentization provides high-reusability and easy verification.
It also makes a system flexible in extensions and specification changes.
There are TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} as a typical component-based development for embedded systems

@@

mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
It is integrated two technologies.
One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS}.
TECS supports to effectively run mruby script language on embedded systems.
mruby on TECS also makes execution time 100 times faster than that of mruby.

This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
mruby on TECS has some problems at present.
One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
Thus that is a big burden on developers.
Another new feature enables developers to run a multitask programs more easily.
Specifically, a cyclic handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

@@

Ruby is a object-oriented script language \cite{url:Ruby}.
As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
Ruby can run a program with fewer code lines than C language.
Ruby improves the productivity of a software development owing to not only simple grammar also object-oriented functions such as classes and methods, exceptions, and garbage collection.

@@

    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
        In the same way, {\it call} ports can be declared.
        Attributes and valuables follow the keyword attr and var respectively.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller{
    call sMotor cMotor;
};
celltype tMotor{
    entry sMotor eMotor;
    attr{
        int32_t attr = 100;
    };
    var{
        int32_t var;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}

    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
        To compose {\it cell}s a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor{
};
cell tCaller Caller{
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.

@@

There is a great difference between the execution time of mruby and C language.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
Thus it is difficult to use mruby for all of code.

@@

\subsection{Component of mruby bytecode loader using Bluetooth}
The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
This generated bytecode is prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:ht-tecs}.
The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.

@@

Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of mruby bytecode loader using Bluetooth, which is like MrubyBluetooth1.
First, a pointer of {\it mrb\_state} structure is initialized.
{\it mrb\_state} is a set of states and global variables used in mruby.
Second, the bytecode of mruby libraries is read.
mruby libraries are a set of Ruby classes such as motor class and sensor class.
For example, motor class defines methods to rotate and stop a motor.
The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: {\it mrubyFile} and {\it irep}.
The {\it mrubyFile} indicates the program files of mruby libraries.
{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
The irep is the pointer of the array stored the bytecode of mruby libraries.
In short the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
Third, the bytecode of the mruby program transferred with Bluetooth is read .
The bytecode transmitted via Bluetooth is stored in an array of type uint8\_t, which is the same as type char.
The array is different from that of holding the mruby library bytecode.
Two bytecodes are read separately in the {\it mrb\_state}.
Finally, an mruby task runs.
When the mruby program is modified, only the bytecode of the modified program should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
    \caption{Control Flow of mruby bytecode loader using Bluetooth}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irepLib=C_EXP("&$cell_global$_irep");
      uint8_t irepApp[COUNT_STK_T(TMAX_APP_BINARY_SIZE)]
              __attribute__((nocommon));
    };
};
\end{lstlisting}
\caption{Celltype Description for mruby bytecode loader using Bluetooth}
\label{celltype_mrubybluetooth}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main(CELLIDX idx)
{
  /* Declaration variables */
  mrb_state *mrb;
  mrbc_context *c;
  /* New interpreter instance */
  mrb = mrb_open();
  // Omit: error check for mrb_state
  /* New mruby context */
  c = mrbc_context_new(mrb);
  // Omit: initialization of mruby-TECS bridge
  /* Receive the bytecode via Bluetooth */
  bluetooth_loader( ATTR_app );
  /* Load mruby library bytecode and run */
  mrb_load_irep_cxt(mrb, ATTR_lib, c);
  /* Load mruby application bytecode and run */
  mrb_load_irep_cxt(mrb, ATTR_app, c);
  if (mrb->exc) {
    /* Failure to execute */
    mrb_p(mrb, mrb_obj_value(mrb->exc));
    exit(0);
  }
  /* Free mruby context */
  mrbc_context_free(mrb, c);
  /* Free interpreter instance */
  mrb_close(mrb);
}

@@

\subsection{Component of Cyclic Handler}
Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configures the cyclic handler based on ITRON.
Cyclic handlers based on ITRON are described in detail \cite{par:microITRON}.
The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
{\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
The attribute is used as an arguments of {\it rotateReadyQueue}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
    \caption{Component Diagram of Cyclic Handler}
    \label{fig:cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
celltype tCyclicHandler {
    [inline] entry sCyclic eCyclic;
    call  siHandlerBody  ciBody;
    attr {
    	[omit] ATR    attribute = C_EXP("TA_NULL");
    	[omit] RELTIM cyclicTime;
    	[omit] RELTIM cyclicPhase = 0;
    };
};
celltype tCyclicMain{
    require tKernel.eiKernel;
    entry siHandlerBody eiBody;
    attr {
        PRI priority;
    };
};
    \end{lstlisting}
    \caption{Celltype Description of Cyclic Handler}
    \label{celltype_cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tCyclicHandler CyclicHandler{
    ciBody = CyclicMain.eiBody;
    attribute = C_EXP("TA_STA");
    cyclicTime = 1;
    cyclicPhase = 1;
};
cell tCyclicMain CyclicMain{
    priority =
        C_EXP("RITEVM_PRIORITY");
};
   \end{lstlisting}
    \caption{Build Description of Cyclic Handler}
    \label{build_cyclic_handler}
\end{figure}

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccc}
        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
        Lua \cite{url:Lua}, \cite{par:Lua} &            & -          & \checkmark &            \\
        Owl system \cite{par:owl}                         &            & -          & -          & \checkmark \\
        mruby \cite{par:mruby}, \cite{url:mruby}                             &            &            & \checkmark &            \\
        mruby on TECS \cite{par:mrubyonTECS}                     &            & \checkmark & \checkmark &            \\
        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
Lua \cite{url:Lua}, \cite{par:Lua}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip \cite{url:python-on-a-chip}.
python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
GIL leads the limitation of the concurrency on multitasking.

@@

In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in muliti-VM.
Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
%%%%%%%%%%%%%
% Reference %
%%%%%%%%%%%%%
\bibliography{ref}
